\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-16 article.tex
another one

As it can be seen on \textit{fig 1}, the raw signal is very noisy due to light
scattering artifacts that ordinarily affects the quality of the recording [in
Stetter, [6]]. Therefore, a low-pass filter is first applied to get a cleaner
version of the signal where only true variations are kept, i.e. without noise
variations. However, the choice of a low-pass filter is not unique. In the
rest of the paper, we will use two particular filters giving similar results,
the symmetrical median filter, i.e., $x^t_i \leftarrow x^{t-1}_i + x^{t}_i +
x^{t+1}_i$, and an asymmetrical weighted median filter taking into account the
history, i.e., $x^t_i \leftarrow 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i
+ x_{t}^i$.

>>>>

As it can be seen on \textit{fig 1}, the raw signal is very noisy due to light
scattering artifacts that ordinarily affects the quality of the recording [in
Stetter, [6]]. Therefore, a low-pass filter is first applied to get a cleaner
version of the signal where only true variations are kept, i.e. without noise
variations. However, the choice of a low-pass filter is not unique. In the
rest of the paper, we will use two particular filters giving similar results,
the symmetrical median filter, i.e., $x^t_i \leftarrow x^{t-1}_i + x^{t}_i +
x^{t+1}_i$, and an asymmetrical weighted median filter taking into account the
history, i.e., $x^t_i \leftarrow 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i
+ x^{t}_i$.
